Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-12-08 manuscript/climate_sensitivity_draft.Rmd
Added snippet on NEON height measurements

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. **IAN- current affliliation**
3. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
4. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada
5. Biological Sciences Department; California State University; Los Angeles, CA 90032, USA
6. Department of Environmental Sciences, University of Virginia, Charlottesville, VA 22903, USA
7. NASA Goddard Space Flight Center; Greenbelt, MD 20771, USA
8. Harvard Forest, Petersham, MA 01366, USA
9. Department of Ecology and Evolutionary Biology; University of California, Los Angeles; Los Angeles, CA 90095, USA
10. Institute of the Environment and Sustainability; University of California, Los Angeles; Los Angeles, CA 90095, USA

@@

Height measurements ($H$, n=1518 trees) were taken by several researchers between 2012 to 2019, and are archived in a public GitHub repository (https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/tree/master/tree_dimensions/tree_heights).**Ian, I think we need to include a little more about the NEON data here.** Measurement methods included manual [@stovall_assessing_2018, NEON], digital rangefinders [@andersonteixeira_size-related_2015], and automatic, ground-based LiDAR [@stovall_terrestrial_2018]. Rangefinders used either the tangent method (Impulse 200LR, TruPulse 360R) or the sine method (Nikon ForestryPro) for calculating heights. Both methods are associated with some error [@larjavaara_measuring_2013], but in this instance there was no clear advantage of one or the other. Species-specific height allometries were developed (Table S2) using logarithmic regression ($ln[H]$). For species with insufficient height data to create reliable species-specific allometries, heights were calculated from an equation developed using all height measurements.

>>>>

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. Center for Geospatial Analytics; North Carolina State University; Raleigh, NC 27607, USA
3. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
4. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada
5. Biological Sciences Department; California State University; Los Angeles, CA 90032, USA
6. Department of Environmental Sciences, University of Virginia, Charlottesville, VA 22903, USA
7. NASA Goddard Space Flight Center; Greenbelt, MD 20771, USA
8. Harvard Forest, Petersham, MA 01366, USA
9. Department of Ecology and Evolutionary Biology; University of California, Los Angeles; Los Angeles, CA 90095, USA
10. Institute of the Environment and Sustainability; University of California, Los Angeles; Los Angeles, CA 90095, USA

@@

Height measurements ($H$, n=1518 trees) were taken by several researchers between 2012 to 2019, and are archived in a public [GitHub repository](https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/tree/master/tree_dimensions/tree_heights). Measurement methods included manual [@stovall_assessing_2018; @neon_national_2018], digital rangefinders [@andersonteixeira_size-related_2015; @neon_national_2018], and automatic, ground-based LiDAR [@stovall_terrestrial_2018]. Rangefinders used either the tangent method (Impulse 200LR, TruPulse 360R) or the sine method (Nikon ForestryPro) for calculating heights. Both methods are associated with some error [@larjavaara_measuring_2013], but in this instance there was no clear advantage of one or the other. Measurements from the National Ecological Observatory Network (NEON) were collected nearby the ForestGEO plot following standard NEON protocol, whereby vegetation of short stature was measured with a collapsible measurement rod, and taller trees with a rangefinder [@neon_national_2018]. Species-specific height allometries were developed (Table S2) using logarithmic regression ($ln[H]$). For species with insufficient height data to create reliable species-specific allometries, heights were calculated from an equation developed using all height measurements.
